---
title: "RAssignment"
author: "Rhys Jenninhgs"
date: "03/05/2020"
output: html_document
---

```{r}
training = read.csv("BankTest.csv")
testing = read.csv("BankTrain.csv")
```


```{r}
glm.fits=glm(y~x1+x2, data=training, family=binomial)

summary(glm.fits)
```
If this is right, the pvalues are s olow for x1 and x2 we can conclude that there is an association between x1/x2 and whether the note has been forged or not. We can see that a one-unit increase in x1 results in decreasing the log odds of being a forged banknote by -1.01(2dp). One unit increase of x2 results in decreasing the log odds of being a forged bank note by -0.28(dp).


- check this stuff agaisnt the weird situation described by the student about less likely to default (look in the textbook)

```{r}
training$x1
```

```{r}



#X1_range <- seq(from=min(training$X1), to=max(training$X), by=.01)
probs <- (exp(0.56697 + (-1.01366*training$x1) + (-0.27964*training$x2))) /(1 + (exp(0.56697 + (-1.01366*training$x1) + (-0.27964*training$x2))))
))

```


```{r}
probs <- (exp(0.56697 + (-1.01366*testing$x1) + (-0.27964*testing$x2))) /(1 + (exp(0.56697 + (-1.01366*testing$x1) + (-0.27964*testing$x2))))



probs[1:10]



```

```{r}
glm.pred = rep("genuine", length(testing$x1))
glm.pred[probs>.5] = "forged"

test_y = rep("genuine", length(testing$y))
test_y[testing$y == 1] = "forged"


table(glm.pred, test_y)
```
Corretly said 372/434 forged notes were forged.
Correctly said 476/526 genuine notes were genuine

So correct for 848/960



```{r}
glm.pred = rep("genuine", length(testing$x1))
glm.pred[probs>.7] = "forged"

table(glm.pred, test_y)



```


```{r}
glm.pred = rep("genuine", length(testing$x1))
glm.pred[probs>.3] = "forged"

table(glm.pred, test_y)


```



```{r}
library(MASS)
lda.fit=lda(y~x1+x2, data=training)
lda.fit
```


```{r}

glm.probsidk <- predict(glm.fits, newdata=testing, type="response")


glm.probsidk[1:10]

probs[1:10]
```












